Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-13 paper/paper.tex
Reordered Bug Reports in Section 8.1
com histograms

\Fix{...add and discuss histograms}

>>>>

To provide a brief overview of the test suites and understand if the engines
have specific testing purposes, we investigated the most common
objects and functions that each one of the JS engines employ.
To achieve this goal, we started by filtering out many non-relevant source
code statements available on the test suites. We started by removing JS language constructs (such as \textt{if}, \textt{for}, and \textt{var}). We then removed
special characters (such as parentheses, mathematical symbols, and semicolons).
For the remaining source code constructs, we search for the ``.'' character, which
indicates a function call. We then stored the function and the object that host
that function.  By manually analyzing this data, we noted many general purpose
functions, that do not provide any hint on the kind of behavior the engine is
more likely to test (such as \texttt{console.log}). We also removed these
general purpose functions. The remaining object/functions are shown at
Figure~\ref{fig:histograms}.

\begin{figure}[thp]
\begin{center}
$
\begin{array}{cc}
Charka & Duktape \\
\includegraphics[width=.5\textwidth, clip, trim= 0px 35px 10px 0px]{figs/hist/chakra.pdf} &
\includegraphics[width=.5\textwidth, clip,trim= 0px 35px 10px 0px]{figs/hist/duktape.pdf} \\
Hermes & JerryJS \\
\includegraphics[width=.5\textwidth, clip,trim= 0px 35px 10px 0px]{figs/hist/hermes.pdf} &
\includegraphics[width=.5\textwidth, clip,trim= 0px 35px 10px 0px]{figs/hist/jerryJS.pdf} \\
JSI & Test262 \\
\includegraphics[width=.5\textwidth, clip,trim= 0px 35px 10px 0px]{figs/hist/jsi.pdf} &
\includegraphics[width=.5\textwidth, clip,trim= 0px 35px 10px 0px]{figs/hist/test262.pdf} \\
TinyJS & V8 \\
\includegraphics[width=.5\textwidth, clip,trim= 0px 35px 10px 0px]{figs/hist/tinyJS.pdf} &
\includegraphics[width=.5\textwidth, clip,trim= 0px 35px 10px 0px]{figs/hist/v8.pdf} \\
\end{array}
$
\end{center}
\caption{histograms.}
\label{fig:histograms}
\end{figure}
